
* unsworth, robison, & miller 2018
  * baseline = 2000ms (fixation)
  * baseline subtracted from 00.000 data
  * averaged into series of 200ms time windows following appearance of numbers
  * phasic responses had last 200ms of ISI subtracted out, divided into 20ms windows
  * peak (usually 550-750ms for PVT) identified, only analyzed if "clear peak is present"
  * fast trials showed greater PD 200-300ms prestim for fix2
  * same seen for fix8, though intercept lower (-.04 vs .01, rather than -.02 vs .04)   * fast responses had larger phasic responses
  * phasic varied: fast peaks at 600ms, .12, slow at 650ms, .04 -- 50ms faster, .08 higher
  * phasic fix2: fast peaks at 550ms, .16, slow at 600ms, .10 -- 50ms faster, .06 higher
  * phasic fix8: fast peaks at 600ms, .14, slow at 650ms, .08 -- 50ms faster, .06 higher

http://www.eyetracking-r.com/vignettes/preparing_your_data
https://cran.r-project.org/web/packages/eyelinker/vignettes/basics.html

```{r}
#devtools::install_github(repo = 'dahtah/eyelinker')
library(eyelinker)
library(eyetrackingR)
library(tidyverse)
library(stringr)
library(magrittr)
theme_set(theme_bw())

#note working directory for .asc files will differ in anna's version
ret1 <- read.asc('~/Desktop/eyetracking/401ret.asc')
names(ret1)

ret2 <- read.asc('~/Desktop/eyetracking/401ret2.asc')
names(ret2)

ret3 <- read.asc('~/Desktop/eyetracking/401ret3.asc')
names(ret3)

ret4 <- read.asc('~/Desktop/eyetracking/401ret4.asc')
names(ret4)
```

* raw: raw data as a function of time
* sac: saccade events
* fix: fixations
* blinks: blinks
* msg: message events
* info: meta-data

```{r}
str(ret1$info)
str(ret2$info)
str(ret3$info)
str(ret4$info)
```

* cr: corneal reflection mode
* input: contains input info
* right: right eye recorded
* mono: monocular recording

```{r}
tail(head(ret1$raw, 30000)) # tons of leading NAs
tail(head(ret2$raw, 30000))
tail(head(ret3$raw, 30000))
tail(head(ret4$raw, 30000))
```

* time: ms
* xp, yp: x and y positions of eye
* ps: pupil size
* cr.info: status of corneal reflection tracking. "..." means good.
* block: .asc file is divided into START and END blocks, indexed here

```{r fig.width = 4, fig.height = 1}
ret1_data <- ret1$raw %>%
  select(time, ps, block) %>%
  drop_na() 

start_time1 <- min(ret1_data$time)

ret1_data %<>% 
  mutate(time = (time - start_time1)/1000)

head(ret1_data)

ggplot(ret1_data, aes(time, ps, color = block)) +
  geom_line() +
  scale_x_continuous(breaks = seq(0, 1380, 60)) +
  xlab('Time (s)') +
  ylab('Pupil Diameter')

ret2_data <- ret2$raw %>%
  select(time, ps, block) %>%
  drop_na() 

start_time2 <- min(ret2_data$time)

ret2_data %<>% 
  mutate(time = (time - start_time2)/1000)

head(ret2_data)

ggplot(ret2_data, aes(time, ps, color = block)) +
  geom_line() +
  scale_x_continuous(breaks = seq(0, 1380, 60)) +
  xlab('Time (s)') +
  ylab('Pupil Diameter')

ret3_data <- ret3$raw %>%
  select(time, ps, block) %>%
  drop_na() 

start_time3 <- min(ret3_data$time)

ret3_data %<>% 
  mutate(time = (time - start_time3)/1000)

head(ret3_data)

ggplot(ret3_data, aes(time, ps, color = block)) +
  geom_line() +
  scale_x_continuous(breaks = seq(0, 1380, 60)) +
  xlab('Time (s)') +
  ylab('Pupil Diameter')

ret4_data <- ret4$raw %>%
  select(time, ps, block) %>%
  drop_na() 

start_time4 <- min(ret4_data$time)

ret4_data %<>% 
  mutate(time = (time - start_time4)/1000)

head(ret4_data)

ggplot(ret4_data, aes(time, ps, color = block)) +
  geom_line() +
  scale_x_continuous(breaks = seq(0, 1380, 60)) +
  xlab('Time (s)') +
  ylab('Pupil Diameter')
```

Zoom in on one minute

```{r}

ggplot(ret1_data %>% filter(between(time, 60, 120)), aes(time, ps, color = block)) +
  geom_line() +
  xlab('Time (s)') +
  ylab('Pupil Diameter')
```

Smooth data

```{r fig.width = 4, fig.height = 1}
ret1_data %<>%
  mutate(smoothed_onset = ksmooth(time, ps, "normal", bandwidth = 3)[[1]],
         smoothed_ps = ksmooth(time, ps, "normal", bandwidth = 3)[[2]]) 

ret1_data %>%
ggplot(aes(smoothed_onset, smoothed_ps, color = block)) +
  geom_line() +
  scale_x_continuous(breaks = seq(0, 1380, 60)) +
  xlab('Time (s)') +
  ylab('Pupil Diameter')
```

```{r}
ret1_events <- ret1$msg %>%
    mutate(time = (time - start_time1)/1000)

ret2_events <- ret2$msg %>%
    mutate(time = (time - start_time2)/1000)

ret3_events <- ret3$msg %>%
    mutate(time = (time - start_time3)/1000)

ret4_events <- ret4$msg %>%
    mutate(time = (time - start_time4)/1000)
```

```{r}
ret1_data %<>% left_join(ret1_events, by = c("block", "time"))

ret2_data %<>% left_join(ret2_events, by = c("block", "time"))

ret3_data %<>% left_join(ret3_events, by = c("block", "time"))

ret4_data %<>% left_join(ret4_events, by = c("block", "time"))
```

```{r}
#input correct block numbers for eventual rbind file

ret2_data$block[ret2_data$block == '1'] <- '4'
ret2_data$block[ret2_data$block == '2'] <- '5'
ret2_data$block[ret2_data$block == '3'] <- '6'

ret3_data$block[ret3_data$block == '1'] <- '7'
ret3_data$block[ret3_data$block == '2'] <- '8'
ret3_data$block[ret3_data$block == '3'] <- '9'

ret4_data$block[ret4_data$block == '1'] <- '10'
ret4_data$block[ret4_data$block == '2'] <- '11'
ret4_data$block[ret4_data$block == '3'] <- '12'
```

```{r}
#create one retrieval file vertically

ret_alldata <- rbind(ret1_data, ret2_data, ret3_data, ret4_data)
```

```{r}
#now bring in csv file with retrieval behavioral info
#note working directory for .csv file will differ in anna's version
ret_behav <- read.csv('~/Desktop/eyetracking/401ret.csv')
names(ret_behav)
```

```{r}
#join ret_behav file with ret_alldata file (to get retrieval behaviors in)

ret_eyesbehav <- merge(ret_alldata,ret_behav, all.x=TRUE)
```

Get time of event markers

```{r}
iti1_times <- ret1_data %>%
  mutate(text = gsub(' ', '', text)) %>%
  drop_na() %>%
  spread(text, time) %>%
  select(starts_with('ITI1')) %>%
  gather(text, time) %>%
  drop_na() %>%
  use_series(time)

iti2_times <- ret1_data %>%
  mutate(text = gsub(' ', '', text)) %>%
  drop_na() %>%
  spread(text, time) %>%
  select(starts_with('ITI2')) %>%
  gather(text, time) %>%
  drop_na() %>%
  use_series(time)

picstim_times <- ret1_data %>%
  mutate(text = gsub(' ', '', text)) %>%
  drop_na() %>%
  spread(text, time) %>%
  select(starts_with('PICSTIM')) %>%
  gather(text, time) %>%
  drop_na() %>%
  use_series(time)

retgoal_times <- ret1_data %>%
  mutate(text = gsub(' ', '', text)) %>%
  drop_na() %>%
  spread(text, time) %>%
  select(starts_with('RETGOAL')) %>%
  gather(text, time) %>%
  drop_na() %>%
  use_series(time)

resp_times <- ret1_data %>%
  mutate(text = gsub(' ', '', text)) %>%
  drop_na() %>%
  spread(text, time) %>%
  select(starts_with('RESP')) %>%
  gather(text, time) %>%
  drop_na() %>%
  use_series(time)

# thinking about which aspects from retrieval csv file to bring in ... need block column, need retgoal_xx, need resp_xx (for each of 21 trials per block); maybe I can organize retrieval csv file in this way to pull in retgoal and resp accuracy for each trial (e.g., // BLOCK 1 // RETGOAL_1 SMAL // RESP_1 HIT //) ... seems confusing to go by onset time in retrieval csv file because we have messages from Eyelink already? 
```

```{r fig.width = 4, fig.height = 1}
ret1_data %>%
ggplot(aes(time, ps, color = block)) +
  geom_line() +
  scale_x_continuous(breaks = seq(0, 1380, 60)) +
  xlab('Time (s)') +
  ylab('Pupil Diameter') +
  geom_vline(xintercept = iti1_times, color = "grey") +
  geom_vline(xintercept = iti2_times, color = "lightgrey") 
```

Zoom in on one minute


```{r fig.height = 2, fig.width = 5}

ggplot(ret1_data %>% filter(between(time, 60, 120)), aes(time, ps)) +
  geom_line(color = "darkgrey") +
  scale_x_continuous(breaks = seq(60, 120, 5)) +
  xlab('Time (s)') +
  ylab('Pupil Diameter') +
  geom_vline(xintercept = iti1_times[between(iti1_times, 60, 120)], color = "turquoise4", linetype = 2) +
  geom_vline(xintercept = iti2_times[between(iti2_times, 60, 120)], color = "plum4", linetype = 2) +
  geom_vline(xintercept = retgoal_times[between(retgoal_times, 60, 120)], color = "turquoise4") +
  geom_vline(xintercept = picstim_times[between(picstim_times, 60, 120)], color = "plum4") +
  geom_vline(xintercept = resp_times[between(resp_times, 60, 120)], color = "magenta")

```

Smooth via time bins
```{r}
ret1_data %<>%
  mutate(time_bin = ntile(time, max(time)))

ret1_data %<>%
  group_by(time_bin) %>%
  mutate(ps_binned = mean(ps))
```


```{r fig.height = 2, fig.width = 5}

ggplot(ret1_data %>% filter(between(time, 60, 120)), aes(time, ps_binned)) +
  geom_line(color = "darkgrey") +
  xlab('Time Bin') +
  ylab('Pupil Diameter') +
  geom_vline(xintercept = iti1_times[between(iti1_times, 60, 120)], color = "turquoise4", linetype = 2) +
  geom_vline(xintercept = iti2_times[between(iti2_times, 60, 120)], color = "plum4", linetype = 2) +
  geom_vline(xintercept = retgoal_times[between(retgoal_times, 60, 120)], color = "turquoise4") +
  geom_vline(xintercept = picstim_times[between(picstim_times, 60, 120)], color = "plum4") +
  geom_vline(xintercept = resp_times[between(resp_times, 60, 120)], color = "magenta")

```

Patterns: 
* PD decreased after goal state onset
* decreased steeply during first ISI
* increased rapidly at onset of pic stim
* stable/slight increase during second ISI

Look at another minute.


```{r fig.height = 2, fig.width = 5}
minute2_times <- function(times) {
  between(times, 120, 180)
}

ggplot(ret1_data %>% filter(minute2_times(time)), aes(time, ps_binned)) +
  geom_line(color = "darkgrey") +
  xlab('Time Bin') +
  ylab('Pupil Diameter') +
  geom_vline(xintercept = iti1_times[minute2_times(iti1_times)], color = "turquoise4", linetype = 2) +
  geom_vline(xintercept = iti2_times[minute2_times(iti2_times)], color = "plum4", linetype = 2) +
  geom_vline(xintercept = retgoal_times[minute2_times(retgoal_times)], color = "turquoise4") +
  geom_vline(xintercept = picstim_times[minute2_times(picstim_times)], color = "plum4") +
  geom_vline(xintercept = resp_times[minute2_times(resp_times)], color = "magenta")
```


Pattern confirmation?
* PD not decreasing at ret goal onset
* still see decrease during ISI
* still increases rapidly at onset of pic stim
* still see stable/slight increase (w/possible dip in the middle) for second ISI
